---
title: "PS07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars, message = FALSE}
library(tidyverse)
library(ggplot2)
skating_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRHL3GBQobQsveBg1-hqydHUPAxx4ni3XmFJmxn1vlvX8B7JGYtnx3OX-uBYVxKI3_khP8LuoFL-wD2/pub?gid=0&single=true&output=csv")
```

# Figure Skating

I am a figure skater and over the last several months I have been collecting data about my practice sessions. After each day of practice, I record:
 
  * The date
  
  * How many of each type of jump I did (numeric)
   
    + `X1A`: single axel
    
    + `X2S`: double salchow
    
    + `X2Lo`: double loop
    
    + `X2T`: double toe-loop
    
    + `X2Fl`: double flip
    
    + `X2fl.2T`: double flip + double toe-loop combination 
    
    + `X2t.2T`: double toe-loop + double toe-loop combination
    
    + `X2Lz`: double lutz
    
    + `X2A`: double axel
 
  * Whether or not I completed my skill dills (Y/N binary)
    
    + `X1T.ladder`: single toe-loop jump ladder
    
    + `X1L.ladder`: single loop jump ladder
 
  * Whether or not I practiced spins (Y/N binary)
    
    + `Spins`
  
  * How many runthroughs of each of my programs I completed (numeric)
    
    + `SP.RT`: short program
    
    + `FP.RT`: freeskate
    
    + `FD.RT`: solor freedance
  
  * How many international pattern ice dances I practiced (numeric)
  
    + `Dances`
  
  * How many sessions I skated 
    
    + `Hours`
 
  * A short refelction of my practice that day
      
## Axel Jumps

The jump that I practice most frequently is the single axel jump. A single axel jump takes off on a forward outside edge (leaning towards the outside of the foot to follow a circle a curve), rotates 1.5 times in the air, and lands on a backwards outside edge on the other foot. 

Here is a graph of the distribution of how many axels I complete on a single day of practice. 

```{r pressure, echo=FALSE}
ggplot(skating_data, aes(x = X1A)) + 
  geom_histogram(binwidth = 1, color = "white") +
  labs(x = "Number of Axel Jumps", y = "Number of Days") +
  ggtitle("Distribution of Daily Total of Axel Jumps")
```

## Skill Drills

### Single Toe-Loop Ladder

The single toe-loop ladder is a skill drill where the skater will complete all single jumps with a single toe-loop combo on each one. A single toe loop jump is a jump that takes off and lands on the backwards outside edge of the same foot. Takeoff is aided using the toe pick of the free leg. 

Here is a graph of how many days I completed the single toe-loop ladder during my practice time since I started collecting data. 

```{r, echo = FALSE}
ggplot(skating_data, aes(x = X1T.ladder)) + 
  geom_bar() +
  labs(x = "Completion Status", y = "Number") +
  ggtitle("Completion Totals for Single Toe-Loop Ladder")
```

### Single Loop Ladder

The single loop ladder is similar to the single toe-loop ladder, but instead the combo is completed with a single loop jump for each single jump pass. A single loop jump is a jump that takes off and lands on the backwards outside edge of the same foot. Takeoff is achieved without help from the toepick of the free leg. 

Here is a graph of how many days I completed the single loop ladder during my practice time since I started collecting data. 

```{r, echo = FALSE}
ggplot(skating_data, aes(x = X1L.ladder)) + 
  geom_bar() +
  labs(x = "Completion Status", y = "Number") +
  ggtitle("Completion Totals for Single Loop Ladder")
```
